\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-08-28 ResponseToReview.tex

\res{We have expanded on this concept in the introduction using \emph{Oryza sativa} as an example: ``For example, \emph{Oryza rufipogon}, the wild progenitor of domesticated rice, has proven useful for the integration of a number of beneficial QTL controlling traits such as grain size and yield into domesticated rice (Kovach and McCouch 2008). Furthermore, in teosinte, many of the alleles underlying domestication phenotypes have been shown to be segregating in populations of teosinte, suggesting that natural variation in teosinte has played an important role in the domestication of maize (Gallavotti \emph{et al.} 2004; Sigmon and Vollbrecht 2010). While some effort has been invested into understanding how wild alleles behave in their domesticated relatives (\emph{e.g.} Bai and Lindhout 2007), very little is known about the role that alleles found most commonly in domesticates play in natural populations of their wild progenitors (Whitton \emph{et al.} 1997).}

8) Page 5, line 12 - 14: You say "The tb1 locus appears to play an important role in the shade avoidance pathway in Zea mays and other grasses and may therefore be crucial to the ecology of teosinte (Kebrom and Brutnell, 2007; Lukens and Doebley, 1999)." Please clarify; do the references belong to the first half of the sentence, supporting tb1 playing a role in Zea mays, or the second half of the sentence, supporting tb1 possibly being crucial to the ecology of teosinte? Which of the two distinct things have actually been studied? If the first, could you tell us how tb1 has been shown to work in maize under shade conditions? If the second, was it actually studied, or merely hypothesized in teosinte?\\

\res{We have moved the references cited here to more clearly reflect the papers' findings.  We have also added text describing the role of \emph{tb1} in the shade avoidance pathway and clarifying the manner in which this could affect fitness in teosinte}

\mbh{References need to follow text saying \emph{tb1} is important in the shade avoidance pathway and we need to add a sentence or two clarifying what it does in this pathway and the implications for teosinte fitness} \lev{the refs are in the sentences discussing the SAS in teo/grasses}

@@

15) Page 7 lines 22 - 23: "We used genotyping and covariance data from Pyhajarvi et al. (2013) for BayEnv" what kind of dataset is this? Teosinte?\\

\res{We have clarified the dataset in the paper: ``We used teosinte (ssp. \emph{parviglumis} and ssp. \emph{mexicana} genotyping and covariance data from Pyh{\"a}j{\"a}rvi \emph{et al.} (2013) for BayEnv, with the \emph{Hopscotch} insertion coded as an additional SNP. SNP data from Pyh{\"a}j{\"a}rvi \emph{et al.} (2013) were obtained using the MaizeSNP50 BeadChip and Infinium® HD Assay (Illumina, San Diego, CA, USA)."}

16) Page 8 lines 20 - 21:" We created haplotype blocks using a custom Perl script that grouped SNPs separated by less than 5kb into haplotypes." Does LD data in your parviglumus support 5Kb?\\

\res{While the recombination landscape will vary to some extent across individuals of teosinte and maize, broad-scale patterns are conserved \citep{bauer2013}.  We therefore relied on previous estimates of the decay of linkage disequilibrium based on data from 102 lines of maize that suggest LD (as measured by $r^2$) will decline to 0.1 within 2,000 bp \citep{remington2001}.  Using this measure, we chose 5kb as a conservative estimate of the extent of linkage disequilibrium in our sample and the physical distance over which SNPs would have to be separated in order to be in weak linkage and not violate assumptions of the STRUCTURE model.}

@@

20) Results:
Page 10 lines 5 - 6: ``Within our parviglumis and mexicana samples we found the Hopscotch insertion segregating in 37 and four populations, respectively"; remind us how many parviglumis and Mexicana samples you had total? So we can see if this comes out to a very different ratio than in maize."\\

\res{We have added ratios to the text: ``Within our \emph{parviglumis} and \emph{mexicana} samples we found the \emph{Hopscotch} insertion segregating in 37 ($n=86$) and four ($n=17$) \mbh{update manuscript to $n=X$ format} populations, respectively, and at highest frequency in the states of Jalisco, Colima, and Michoac\'{a}n in central-western Mexico."}

21) Page 10 lines 7 - 9: ``Using our Hopscotch genotyping, we calculated diﬀerentiation between populations (FST) and subspecies (FCT) for populations in which we sampled eight or more alleles." What do you mean, 8 or more alleles? I thought you only had presence or absence; how are alleles differentiated with your PCR?\\

\res{Please see our response to point 12.  We developed a co-dominant assay that was capable of detecting whether an individual was homozygous or heterozygous for the \emph{Hopscotch} insertion or lacked the insertion entirely.  We have also edited this to read ``eight or more chromosomes" which is a more precise description of our methodology.}
\mbh{update the text in the manuscript}
